
##Columns Explaination
1) ID = internal kickstarter id
2) name = name of project - A project is a finite work with a clear goal that you’d like to bring to life. Think albums, books, or films.
3) category = category
4) main_category = category of campaign
5) currency = currency used to support
6) deadline = deadline for crowdfunding
7) goal = fundraising goal - The funding goal is the amount of money that a creator needs to complete their project.
8) launched = launched date launched
9) pledged = amount pledged by "crowd"
10) state = Current condition the project is in
11) backers = number of backers
12) country = country pledged from
13) usd pledged = amount of money pledged

```{r}
KickStar <- read.csv("C:/Users/ericv/OneDrive/Documents/MGSC310/ks-projects-201612.csv")

KickStar$goal <- as.numeric(KickStar$goal)
KickStar$pledged <- as.numeric(KickStar$pledged)
KickStar$state <- factor(KickStar$state, levels = c("failed", "successful", "canceled", "live", "undefined", "suspended"))
KickStar$currency <- factor(KickStar$currency, levels = c("USD", "GBP", "CAD", "EUR", "AUD", "SEK"))
KickStar$country <- factor(KickStar$country, levels = c("US", "GB", "CA", "AU", "DE", "IE", "IT","NZ","NL","SG", "SE", "NO","MX", "FR", "BE", "ES"))
KickStar$usd.pledged <- as.numeric(KickStar$usd.pledged)
KickStar<- KickStar[!is.na(KickStar$currency),]
KickStar<- KickStar[!is.na(KickStar$country),]
colSums(is.na(KickStar))
sum(is.na(KickStar$currency))
sum(is.na(KickStar$state))
summary(KickStar)


```

```{r}
#install.packages("ggplot2")
library(ggplot2)

#ggplot of Goal Amount and Pledge Amount
ggplot(data = KickStar, aes(goal, pledged)) + geom_smooth() + facet_wrap(~state) + labs(title = "Smooth Plot of Goal vs Pledge Amount") + labs(x = "Goal Amount", y = "Pledge Amount")

colSums(is.na(KickStar))
sum(is.na(KickStar$currency))
sum(is.na(KickStar$state))

ggplot(data = KickStar, aes(x = currency, y = usd.pledged)) + geom_bar(stat = "identity") + labs(x = "Type of Currency", y = "Amount of $ Pledged") + labs(title = "Amount Pledged by Currency")


ggplot(data = KickStar, aes(category)) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Count of Categories", x = "Categories", y = "Count")

ggplot(data = KickStar, aes(state)) + geom_bar() + labs(title = "Counts per State")


ggplot(data = Kickstart, aes(group = cut_width(year, 10)), scale = "width") + geom_violin()

```







