#Kickstarter Data

##Columns Explanation
1) ID = internal kickstarter id
2) name = name of project - A project is a finite work with a clear goal that you’d like to bring to life. Think albums, books, or films.
3) category = category
4) main_category = category of campaign
5) currency = currency used to support
6) deadline = deadline for crowdfunding
7) goal = fundraising goal - The funding goal is the amount of money that a creator needs to complete their project.
8) launched = launched date launched
9) pledged = amount pledged by "crowd"
10) state = Current condition the project is in
11) backers = number of backers
12) country = country pledged from
13) usd pledged = amount of money pledged

##Packages Needed to Download
```{r}
#install.packages("ggplot2")
library(ggplot2)

library(doBy)

#install.packages("useful")
library(useful)

library(glmnet)

#install.packages('rpart')
library(rpart)

#install.packages("randomForest")
library("randomForest")

set.seed(1861)
```

```{r}
#reads in data into KickStar
KickStar <- read.csv("/Users/Cheddar3/Desktop/MGSC310/Group Projects/kickstarter-projects/ks-projects-201612.csv")

#removing a few columns with null values
KickStar <- subset(KickStar, select = -c(14,15,16,17))
#colSums(is.na(KickStar))
KickStar<- KickStar[!is.na(KickStar$name),]
#colSums(is.na(KickStar))

#cleaning up category column
KickStar$category <- factor(KickStar$category, levels = c("Zines","Young Adult", "World Music", "Workshops" ,"Woodworking", "Webseries", "Webcomics", "Web","Weaving", "Wearables", "Video Games", "Video Art", "Video", "Vegan", "Typography", "Translations", "Thrillers", "Theater", "Textiles", "Television", "Technology", "Taxidermy", "Tabletop Games", "Stationery", "Spaces", "Space Exploration", "Sound", "Software", "Small Batch", "Shorts", "Sculpture", "Science Fiction", "Romance", "Rock", "Robots", "Restaurants", "Residencies", "Ready-to-wear", "Radio & Podcasts", "R&B", "Quilts", "Puzzles", "Punk", "Publishing", "Public Art", "Product Design", "Printing", "Print", "Pottery", "Pop", "Poetry", "Plays", "Playing Cards", "Places", "Photography", "Photobooks", "Photo", "Pet Fashion", "Periodicals", "Performances", "Performance Art", "People", "Painting", "Nonfiction", "Nature", "Narrative Film", "Musical", "Music Videos", "Music", "Movie Theaters", "Mobile Games", "Mixed Media", "Metal", "Makerspaces", "Live Games", "Literary Journals", "Letterpress", "Latin", "Knitting", "Kids", "Journalism", "Jewelry", "Jazz", "Interactive Design", "Installations", "Indie Rock", "Immersive", "Illustration", "Horror", "Hip-Hop", "Hardware", "Graphic Novels", "Graphic Design", "Glass", "Gaming Hardware", "Games", "Gadgets", "Footwear", "Food Trucks", "Food", "Flight", "Fine Art", "Film & Video", "Fiction", "Festivals", "Fashion", "Farms", "Farmer's Markets", "Fantasy", "Family", "Faith", "Fabrication Tools", "Experimental", "Events", "Embroidery", "Electronic Music", "Drinks", "Drama", "Documentary", "DIY Electronics", "DIY", "Digital Art", "Design", "Dance", "Crochet", "Crafts", "Couture", "Country & Folk", "Cookbooks", "Conceptual Art", "Community Gardens", "Comics", "Comic Books", "Comedy", "Classical Music", "Civic Design", "Chiptune", "Childrenswear", "Children's Books", "Ceramics", "Candles", "Camera Equipment", "Calendars", "Blues", "Bacon", "Audio", "Art Books", "Art", "Architecture", "Apps", "Apparel", "Anthologies", "Animation", "Animals", "Action", "Accessories", "Academic", "3D Printing"))
#colSums(is.na(KickStar))
KickStar<- KickStar[!is.na(KickStar$category),]
#colSums(is.na(KickStar))

#cleaning main_category column
#table(KickStar$main_category)
KickStar$main_category <- factor(KickStar$main_category, levels = c("Theater", "Technology", "Publishing", "Photography", "Music", "Journalism", "Games", "Food", "Film & Video", "Fashion", "Design", "Dance", "Crafts", "Comics", "Art"))
#colSums(is.na(KickStar))

#clearning currency column
#table(KickStar$currency)
KickStar$currency <- factor(KickStar$currency, levels = c("USD", "SGD", "SEK", "NZD", "NOK", "MXN", "HKD", "GBP", "EUR", "DKK", "CHF", "CAD", "AUD"))
#colSums(is.na(KickStar))

#cleaning goal column
KickStar$goal <- as.numeric(KickStar$goal)
#colSums(is.na(KickStar))

#cleaning pledge column
KickStar$pledged <- as.numeric(KickStar$pledged)

#cleaning state column
#table(KickStar$state)
KickStar$state <- factor(KickStar$state, levels = c("failed", "successful"))
#colSums(is.na(KickStar))
KickStar<- KickStar[!is.na(KickStar$state),]
#colSums(is.na(KickStar))

#cleaning backers column
KickStar$backers <- as.numeric(KickStar$backers)
#colSums(is.na(KickStar))

#cleaning country column
#table(KickStar$country)
KickStar$country <- factor(KickStar$country, levels = c("US", "SG", "SE", "NZ", "NO", "NL", "MX", "LU", "IT", "IE", "HK", "GB", "FR", "ES", "DK", "DE", "CH", "CA", "BE", "AU", "AT"))
#colSums(is.na(KickStar))
KickStar<- KickStar[!is.na(KickStar$country),]
#colSums(is.na(KickStar))

#cleaning usd.pledged column
KickStar$usd.pledged <- as.numeric(KickStar$usd.pledged)
#colSums(is.na(KickStar))

#creates deadline and launched variable so its just year/month/day
KickStar$newDeadline <- as.Date(as.POSIXlt(KickStar$deadline, origin = "1582-10-14",tz = "GMT"))
KickStar$newLaunched <- as.Date(as.POSIXlt(KickStar$launched, origin = "1582-10-14",tz = "GMT"))

#difference between launched and deadline in days
KickStar$DateDiffDays <- KickStar$newDeadline - KickStar$newLaunched

#if successful, then 1, else 0
KickStar$binomState <- ifelse(KickStar$state == "successful",1,0)

trainSize <- 0.75
trainInd <- sample(1:nrow(KickStar), size = floor(nrow(KickStar) * trainSize))
KickTrain <- KickStar[trainInd, ]
KickTest <- KickStar[-trainInd, ]

#gets summary of data
summary(KickStar)
```



```{r}
#ggplot of Goal Amount and Pledge Amount by state of company
ggplot(data = KickStar, aes(goal, pledged)) + geom_smooth() + facet_wrap(~state) + labs(title = "Smooth Plot of Goal vs Pledge Amount by State of Company") + labs(x = "Goal Amount", y = "Pledge Amount")

#ggplot of Goal Amount and Pledge Aamount by country
ggplot(data = KickStar, aes(goal, pledged)) + geom_smooth() + facet_wrap(~country) + labs(title = "Smooth Plot of Goal vs Pledge Amount by Country") + labs(x = "Goal Amount", y = "Pledge Amount")

#ggplot of bar graph with type of currency and the amount pledged 
ggplot(data = KickStar, aes(x = currency, y = usd.pledged)) + geom_bar(stat = "identity") + labs(x = "Type of Currency", y = "Amount of $ Pledged") + labs(title = "Amount Pledged by Currency")

##ggplot of bar graph of count of each categories
ggplot(data = KickStar, aes(category)) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(title = "Count of Categories", x = "Categories", y = "Count")

#ggplot of bar graph of count by state 
ggplot(data = KickStar, aes(state)) + geom_bar() + labs(title = "Counts per State")
```


#Logistic Regression Models

##Using the training data to create a model

###Find summary statistics when the Kickstarter succeed (1) or did not (0)
```{r}
summaryBy(goal + pledged + backers + currency ~ binomState, data = KickTrain, fun = c(mean,sd))
```
It appears that Kickstarters that had less funding, less pledges, less currency, and less backers failed.


###Creating a glm model on the training data and summary
```{r}
glmmodTrain <- glm(binomState ~ goal + pledged + backers + DateDiffDays + currency, data = KickTrain, family = binomial)
summary(glmmodTrain)
```

###Find odds ratios
```{r}
exp(glmmodTrain$coefficients)
```


###Plotting the model
```{r}
plot(glmmodTrain)
```

###Creating probabilty of failure (1) or not (0)
```{r}
glmTrainProbs <- predict.glm(glmmodTrain, type = "response")
hist(glmTrainProbs)
```

```{r}
table(KickStar$binomState)

glmTrainPreds <- rep("Failed", nrow(KickTrain))
glmTrainPreds[glmTrainProbs > 0.5] <- "Succeed"
conftab <- table(glmTrainPreds, true = KickTrain$binomState)
print(conftab)
```

```{r}
TPtrain <- conftab[2, 2]/(conftab[1, 2] + conftab[2, 2])
TNtrain <- conftab[1, 1]/(conftab[1, 1] + conftab[2, 1])
FPtrain <- conftab[2, 1]/(conftab[2, 1] + conftab[1, 1])
FNtrain <- conftab[1, 2]/(conftab[1, 1] + conftab[2, 1])
```

##Using the TESTING data to create a model


###Find summary statistics when the Kickstarter failed (1) or did not fail (0)
```{r}
summaryBy(goal + pledged + backers + currency + DateDiffDays ~ binomState, data = KickTest, fun = c(mean,sd))
```
It appears that Kickstarters that had less funding, less pledges, less currency, and less backers failed.


###Creating a glm model on the training data and summary
```{r}
glmmodTest <- glm(binomState ~ goal + pledged + backers + DateDiffDays + currency, data = KickTest, family = binomial)
summary(glmmodTest)
```

###Find odds ratios
```{r}
exp(glmmodTest$coefficients)
```


###Plotting the model
```{r}
plot(glmmodTest)
```

###Creating probabilty of failure (1) or not (0)
```{r}
glmTestProbs <- predict.glm(glmmodTest, type = "response")
hist(glmTestProbs)
```

```{r}
glmTestPreds <- rep("Failed", nrow(KickTest))
glmTestPreds[glmTestProbs > 0.5] <- "Succeed"
conftabTest <- table(glmTestPreds, true = KickTest$binomState)
print(conftabTest)
```

```{r}
TPtest <- conftabTest[2, 2]/(conftabTest[1, 2] + conftabTest[2, 2])
TNtest <- conftabTest[1, 1]/(conftabTest[1, 1] + conftabTest[2, 1])
FPtest <- conftabTest[2, 1]/(conftabTest[2, 1] + conftabTest[1, 1])
FNtest <- conftabTest[1, 2]/(conftabTest[1, 1] + conftabTest[2, 1])

#TRAINING RESULTS 
print(TPtrain)
print(TNtrain)
print(FPtrain)
print(FNtrain)

#TESTING RESULTS
print(TPtest)
print(TNtest)
print(FPtest)
print(FNtest)
```

###Test vs Training MSE
```{r}
#Might not need to do this because "prediction from a rank-deficient fit may be misleadingprediction from a rank-deficient fit may be misleading"
predictKickTrainLogistic <- predict(glmmodTrain, newdata = KickTrain, type = "response")
KickTrainLogisticMSE = mean((KickTrain$binomState - predictKickTrainLogistic)^2)

predictKickTestLogistic <- predict(glmmodTest, newdata = KickTest, type = "response")
KickTestLogisticMSE = mean((KickTest$binomState - predictKickTestLogistic)^2)


print(KickTrainLogisticMSE)
print(KickTestLogisticMSE)
```


#Lasso, Ridge, Elastic Net Models

```{r}
myFormula <- as.formula(binomState ~ main_category + currency + goal + pledged + backers + country + usd.pledged + DateDiffDays)

Xvar <- build.x(myFormula, KickTrain) 
Yvar <- build.y(myFormula, KickTrain)


LassoMod <- cv.glmnet(x = Xvar, y = Yvar, alpha = 1, nfolds = 10)
plot(LassoMod)

#Ridge Mod.
RidgeMod <- cv.glmnet(x = Xvar, y = Yvar, alpha = 0, nfolds = 10)
plot(RidgeMod)

#Elastic Net
ElasticNet1 <- cv.glmnet(x = Xvar, y = Yvar, alpha = .25, nfolds = 10)
ElasticNet2 <- cv.glmnet(x = Xvar, y = Yvar, alpha = .50, nfolds = 10)
ElasticNet3 <- cv.glmnet(x = Xvar, y = Yvar, alpha = .75, nfolds = 10)
plot(ElasticNet1)

#MSE
MSE <- function(true, preds) { mean((true - preds)^2) }
MSE(KickTrain$binomState, predict(LassoMod, newx = Xvar))
MSE(KickTrain$binomState, predict(RidgeMod, newx = Xvar))
MSE(KickTrain$binomState, predict(ElasticNet1, newx = Xvar))
MSE(KickTrain$binomState, predict(ElasticNet2, newx = Xvar))
MSE(KickTrain$binomState, predict(ElasticNet3, newx = Xvar))

```

###Tree Based Methods
```{r}
newKickStar <- subset(KickStar, select = -c(1,2,3,4,5,6,8,12,14,15))
trainSize <- .02
trainInd <- sample(1:nrow(newKickStar), size = floor(nrow(newKickStar) * trainSize))
newKickTrain <- newKickStar[trainInd, ]
newKickTest <- newKickStar[-trainInd, ]
```


```{r}
#README!!! make sure you click the green arrow to run this properly
#method = class for classification problem
tree <- rpart(state ~ .-binomState, data = newKickTrain, method = "class", control = rpart.control(minsplit=30,  cp=0.01))
par(xpd=TRUE)
print(tree)
plot(tree) 
text(tree, pretty = 0)
```

##Pruning Tree
```{r}
# HAVENT TOUCHED THIS YET 
# predict using the test data
tree.pred <- predict(tree.carseats,Carseats[-train,],type="class")
# note with() command evaluates an R expression in an environment 
# constructed from the data, 
with(Carseats[-train,],table(tree.pred,High))

require('ISLR')
require('tree')

# now do some cross-validating
cv.kick = cv.tree(tree,FUN=prune.misclass)
cv.carseats
plot(cv.carseats)
prune.carseats=prune.misclass(tree.carseats,best=13)
plot(prune.carseats);text(prune.carseats,pretty=0)

# now let's evaluate this pruned tree on the dataset
tree.pred = predict(prune.carseats, Carseats[-train,],type="class")
with(Carseats[-train,],table(tree.pred,High))
(72+32)/150

```




###WORK ON THIS LATER
```{r}
MSE <- function(truth, predict) {mean((truth - predict)^2)}
predsTrain <- predict(tree, newdata = newKickTrain)
predsValidate <- predict(tree, newdata = newKickTest)
MSE(newKickStar$binomState, predsTrain)
MSE(newKickStar$binomState, predsValidate)
```

###Random Forest

WEBSITE USED: https://www.statmethods.net/advstats/cart.html

```{r}
randTree <- randomForest(state ~ ., data=newKickTrain, mtry=3, method = "class")
importance(randTree)
plot(randTree)
```








